Process Genotypes For Ancestry Analysis

### 2019-09-19 code/Ancestry_PCA.Rmd
Clean

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
CORES=$(nproc)

wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

@@

tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz

for i in {1..22}
do
    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
done

bcftools concat --threads $CORES chr22.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr21.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr20.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr19.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr18.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr17.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr16.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr15.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr14.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr13.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr12.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr9.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr11.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr10.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr8.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr7.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr6.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr5.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr4.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr3.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr2.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr1.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz -O z > phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

rm chr*.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

plink --vcf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz --threads $CORES --make-bed --out 1000Genomes
rm phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

>>>>

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/

CORES=`expr $(nproc) - 2`

#ID Sample list of needed Ref Populations
wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/

@@

#i=22
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
    rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf

done

#Merge All Plink Files into genome wide
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.List
done

plink --bfile 1000Genomes_chr1 --merge-list Merge.List --make-bed --out 1000Genomes_Merged
rm 1000Genomes_chr*
